---
title: "Biomass_speciesFactorial"
author: "emcintir"
date: "02 December 2021"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'
```

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see https://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
#This script is for running the species traits factorial design. 
# it requires a version of Biomass_core that is gitIgnored. The versino had many changes to accomodate the 'no regeneration' scenario
# Many of the other changes have been subsequently incorporated into Biomass_core, so it may work with a newer version
options(reproducible.showSimilar = TRUE, 
        reproducible.useMemoise = FALSE, reproducible.cacheSaveFormat = "qs", spades.moduleCodeChecks = FALSE,
        reproducible.showSimilarDepth = 5, spades.recoveryMode = FALSE)

# Packages
if (!require("Require")) {install.packages("Require"); require("Require")}
Require("PredictiveEcology/SpaDES.install", upgrade = FALSE)
installSpaDES()
Require(c("PredictiveEcology/SpaDES.core@development (== 1.0.9.9004)",
          "reproducible"), upgrade = FALSE)

# Modules
setPaths(rasterPath = "temp",
         cachePath =  file.path("temp/Cache"),
         modulePath = file.path("modules"),
         inputPath = file.path(getwd(), "inputs"),
         outputPath = file.path(getwd(),"outputs"))

moduleNameAndBranch <- c("Biomass_speciesParameters@EliotTweaks",
                         "Biomass_speciesFactorial@main"#, "Biomass_borealDataPrep@development", 
                         #"Biomass_core@development"
                         )
lapply(moduleNameAndBranch, function(modName) {
  Cache(getModule, file.path("PredictiveEcology", modName), #modulePath = getPaths()$modulePath, 
        overwrite = TRUE)
})
modules <- gsub("@.+", "", moduleNameAndBranch)
modules <- c("Biomass_speciesFactorial", modules)

outputs <- data.frame(expand.grid(objectName = c("species", "speciesEcoregion"),
                                  saveTime = 0,
                                  eventPriority = 10, fun = "qs::qsave",
                                  stringsAsFactors = FALSE))

# Slow and large
objects <- list(argsForFactorial = list(cohortsPerPixel = 1:2,
                                        growthcurve = seq(0.65, 0.85, 0.02),
                                        mortalityshape = seq(20, 25, 1),
                                        longevity = seq(125, 400, 25), # not 600 -- too big
                                        mANPPproportion = seq(3.5, 6, 0.25))
)

# Fast
objects <- list(argsForFactorial = list(cohortsPerPixel = 1:2,
                                        growthcurve = seq(0.65, 0.85, 0.1),
                                        mortalityshape = seq(20, 25, 5),
                                        longevity = seq(125, 600, 100),
                                        mANPPproportion = seq(3.5, 6, 1))
)
# Medium
objects <- list(argsForFactorial = list(cohortsPerPixel = 1:2,
                                        growthcurve = seq(0.65, 0.85, 0.02),
                                        mortalityshape = seq(20, 25, 2),
                                        longevity = seq(125, 600, 50),
                                        mANPPproportion = seq(3.5, 6, 0.3))
)

simOut <- simInitAndSpades(
  times = list(start = 0, end = 0), # params = parameters, 
  modules = modules, 
  params = list(Biomass_speciesFactorial = list(.plots = NA,#"pdf",
                                                runExperiment = T),
                Biomass_speciesParameters = list(.plots = "pdf")),
  outputs = outputs,
  objects = objects,
  debug = 1
)




```

